Corticosteroids for HELLP syndrome

### 2023-10-21 manuscript.qmd
Update manuscript.qmd
V1.2

Asmaa Fahmy Kasem, Hamdy Bakry Alqenawy, Rania Gamal, Marwa Abd Elmawla Elgendi, Yasser M. Elrefaey, Rowyna Hany Mohamed El Helw, Rania Hassan Mostafa Ahmed, Radwa Rasheedy, Mohammad Nahel Sorour, Mohamed Sameh Elsewefy, Maya M. Abdelrazek, Mohamed Yasser Galal Albahaie, Khadiga Mostafa Hussein Hegab, Mohamed Salama, Ashraf Nabhan

@@

Department of Obstetrics and Gynecology, Faculty of medicine, Ain Shams University, Cairo, Egypt

@@

Hamdy Bakry Alqenawy

@@

**Word count**: xxxx

@@

@@

|--------------------------------|---------------------------|-------------|-------------------------------------------|--------------------------------------------------------------------------------------------|---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|

>>>>

Asmaa Fahmy Kasem^1^, Hamdy Bakry Alqenawy^1^ ^\*^, Marwa Abd Elmawla Elgendi^1^, Radwa Rasheedy^1^, Rania Gamal^1^, Yasser M. Elrefaey^1^, Rowyna Hany Mohamed El Helw^1^, Rania Hassan Mostafa Ahmed^1^, Mohammad Nahel Sorour^1^, Mohamed Sameh Elsewefy^1^, Maya M. Abdelrazek^1^, Mohamed Yasser Galal Albahaie^1^, Khadiga Mostafa Hussein Hegab^1^, Mohamed Salama^1^, Ashraf Nabhan^1^

@@

^1^Department of Obstetrics and Gynecology, Faculty of medicine, Ain Shams University, Cairo, Egypt

@@

^\*^Hamdy Bakry Alqenawy

@@

**Word count**: 3109

@@

+--------------------------------+---------------------------+-------------+-------------------------------------------+--------------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+

@@

+================================+===========================+=============+===========================================+============================================================================================+===============================================================================================================================================================================================================================================================================================================================================================================================================+
